LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-10-04 text/draft.tex
Write the "wait too much" end

\begin{itemize}
	\item \glink{Wait 1}{Wait}
	\item \glink{Go 1}{Go}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait 1}{Wait}
	\item \glink{Go 2}{Go}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait 1}{Listen}
	\item \glink{Go 3}{Go!}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait 1}{Have a drink}
	\item \glink{Go 3}{Just go!}
\end{itemize}

@@

>>>>

\begin{itemize}
	\item \glink{Wait}{Wait}
	\item \glink{Go 1}{Go}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait}{Wait}
	\item \glink{Go 2}{Go}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait}{Listen}
	\item \glink{Go 3}{Go!}
\end{itemize}

@@

\begin{itemize}
	\item \glink{Wait}{Have a drink}
	\item \glink{Go 3}{Just go!}
\end{itemize}

@@

\gsection{Wait}

\dcomment{
	Abrupt fade to black
}

I awake lying in an uncomfortable position in an unknown seat. My head is heavy and aches, my mouth furred, my throat hurting. I believe I've never felt that bad, both mentally and physically, before.\\

I remember delaying, postponing, pushing back, assuring myself I would go after that last song, that last cup, my will to move actually decreasing as time passed on and alcohol filled up my body. I don't know which of my mind or my organism forfeited first, but at some point my memories cease. I suppose I have drunk myself to sleep, with or without an active period of loss of control.\\

And, worse of all, is that \emph{she} was the one who awoke me. Concern is reflecting in her eyes, as she hands me a flask of water. She seems tired, but is ready for departure, fully clothed and equipped.\\

I drink a little. The fresh liquid helps me discard my forgetful stupor in favor of the painful reality. I excuse myself pitifully, ask her to wait for me while I fetch my belongings. I use this time to do a lighting flash toilette and a few minutes later, I'm back and ready to go.\\

After that, I guess I did a bad joke about not knowing my own limits and them we moved on. In the end, the cold facts are that we have a long trip ahead of us, and we already are several hours behind our schedule.\\

As the walk goes on under the light on the sun, she starts shining, the physical effort purifying her body, her pace sure and quick, her cheeks pinkish from the extra ardor put into the back-and-forth sprints she regularly does for scouting ahead. She quickly is as radiant as ever, if not more.\\

Me? I'm slow, gloom and depressed. Not only do I not emit any light, but I'm unable to simply reflect it. I'm a moving piece of darkness, night terrors and regrets. I hate myself for my cowardice, yet I still cannot get rid of it.\\

So I do what I do best. I absorb my own shadows, lock them deep inside me, force myself to smile, to display a happy and optimistic face. I lie to myself than this is only one missed opportunities, that there will be others, than I can still find the courage I missed that time.\\

And as I am a very good liar, I almost convince myself.
